### 2011-11-19 doc/theses/vitasek/diplomka.tex
Thesis: fixing the bibliography again.
Thesis: merging Kesy round 1.

\def\mfauthor{Matej Vitásek}
\def\mfadvisor{RNDr. Ire\-na Mlýn\-ko\-vá Ph.D.}
\def\mfplacedate{Praha, 2011}

@@

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Ms. Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HV}.

@@

Abstract: In this work we~expand upon the~previous efforts to~infer schema information from existing XML documents. We find the~inference of~\textit{structure} to~be~sufficiently researched and focus further on~\textit{integrity constraints}. After briefly introducing some of~them we turn our attention to~ID/\.IDREF/\.IDREFS attributes in~DTD. Building on~the~research by~Barbosa and Menelzon (2003) we~introduce a~heuristic approach to~the~problem of~finding optimal ID set. The~approach is~evaluated and tuned in~a~wide range of~experiments.

@@

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\nocite{*}
\bibliographystyle{alpha}
\bibliography{literature}
%	\include{bibliography}

>>>>

\def\mfauthor{Matej Vitásek}
\def\mfadvisor{RNDr. Ire\-na Mlýn\-ko\-vá, Ph.D.}
\def\mfplacedate{Praha, 2011}

@@

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Irena Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HV}.

@@

Abstract: In this work we~expand upon the~previous efforts to~infer schema information from existing XML documents. We find the~inference of~\textit{structure} to~be~sufficiently researched and focus further on~\textit{integrity constraints}. After briefly introducing some of~them we turn our attention to~ID/\.IDREF/\.IDREFS attributes in~DTD. Building on~the~research by~Barbosa and Menelzon (2003) we~introduce a~heuristic approach to~the~problem of~finding an~optimal ID set. The~approach is~evaluated and tuned in~a~wide range of~experiments.

@@

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
%\nocite{*}
%\bibliographystyle{alpha}
%\bibliography{literature}
	\include{bibliography}
